
---
header-includes:
- \renewcommand{\familydefault}{\sfdefault}
- \usepackage{fancyhdr}
- \usepackage{lastpage}
- \usepackage{datetime}
- \definecolor{blue_AA}{rgb}{0.23,0.30,0.68}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \pagestyle{fancy}
- \fancyfoot[L]{\color{blue_AA}{\today, \currenttime}}
- \fancyfoot[C]{\color{blue_AA}{Page \thepage\ / \pageref{LastPage}}}
- \fancyfoot[R]{\color{blue_AA}{Confidential}}
- \fancyhead[L]{\color{blue_AA}{\textbf{Test for Github} \\\Large{\textit{Report Title - Project Title}}}}
- \fancyhead[R]{\includegraphics[width=1.5cm]{./logo.png}}
- \fancypagestyle{plain}{\pagestyle{fancy}}
- \renewcommand{\footrulewidth}{0.5pt}
- \geometry{a4paper, left=20mm, right=20mm, headheight=3cm, top=3cm, bottom=3 cm,footskip=2cm}
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes

params:
  Version: 1
classoption: table
---

\begin{center}
\end{center}

\vspace{6\baselineskip}

\definecolor{lightgray}{gray}{0.9}
\newcolumntype{g}{>{\columncolor{lightgray}}c}

\begin{center}
\begin{tabular}{|g|l|}
\hline
\textcolor{blue_AA}{Project name} & Github Project \\
\textcolor{blue_AA}{\textit{ }} &  \\\hline
\textcolor{blue_AA}{R Software Version } & `r R.Version()$version.string`\\
\textcolor{blue_AA}{\textit{ }} &  \\\hline
\textcolor{blue_AA}{Version}  & V1 \\
\hspace{5cm} &\hspace{10cm} \\\hline
\textcolor{blue_AA}{Change description } & Initial redaction \\
\textcolor{blue_AA}{ } & \\ \hline
\end{tabular}

\vspace{4\baselineskip}

\begin{tabular}{|g|c|c|c|c|}
\hline
\rowcolor{lightgray} 
&\textcolor{blue_AA}{ \textit{First Name}}  &\textcolor{blue_AA}{ \textit{Last Name } }   &\textcolor{blue_AA}{ Date }   \\
\rowcolor{lightgray} &  & &  \\\hline
\textcolor{blue_AA}{Written by }& Andrés  & Acuña Marroquín & \today  \\ 
\textcolor{blue_AA} {\textit{}} &  &   & 
\\\hline
\end{tabular}

\vspace{4\baselineskip}

\end{center}

\newpage
\centering
\raggedright
\tableofcontents  
 
 
# Definitions 

Definitions : 

+ **The standard deviation:**

The standard deviation quantifies the variation within a set of measurements.
Must not be confused with the standard error. The standard deviation is the most used.


$$ \Large  s = \sqrt{\frac{\sum_{i= 1}^n (x - \bar{x})^2 }{ n - 1 }}   $$

+ **The standard error:**

The  standard error quantifies the variation (standard deviation) of an estimated parameter (or statistic) from a sampling distribution. This is the distribution of the means.  
Can be estimated with a single set of measurments.

$$ \Large Standard\;Error = SE = \frac{s}{\sqrt{n}} $$

+ **The coefficient of variation:** 

The coefficient of variation, also known as relative standard deviation, is a standardized measure of dispersion of a probability distribution.

The coefficient of variation in absolute value : 

$$ CV = \frac{\sigma}{\overline{x}} $$

+ **The coefficient of variation in percentage :**

$$ CV_{\%} = \frac{\sigma}{\overline{x}}*100 $$

+ **R programming language**: R is a programming language for statistical computing and graphics supported by the R Core Team and the R Foundation for Statistical Computing.

\newpage
\newpage
# Introduction
## Purpose

The purpose of this document is to:  


```{r}
source("libraries.R");source("FUN.R")

```


\newpage

# Session Info

```{r,echo=T}

sessionInfo()

```
