
---
header-includes:
- \renewcommand{\familydefault}{\sfdefault}
- \usepackage{fancyhdr}
- \usepackage{lastpage}
- \usepackage{datetime}
- \usepackage{xcolor}
- \definecolor{red_AA}{RGB}{255,120,120}
- \pagestyle{fancy}
- \fancyfoot[L]{\color{red_AA}{\today, \currenttime}}
- \fancyfoot[C]{\color{red_AA}{Page \thepage\ / \pageref{LastPage}}}
- \fancyfoot[R]{\color{red_AA}{Confidential}}
- \fancyhead[L]{\color{red_AA}{\textbf{Test for Github} \\\Large{\textit{Report Title - Project Title}}}}
- \fancyhead[R]{\includegraphics[width=1.5cm]{./logo.png}}
- \fancypagestyle{plain}{\pagestyle{fancy}}
- \renewcommand{\footrulewidth}{0.5pt}
- \geometry{a4paper, left=20mm, right=20mm, headheight=3cm, top=3cm, bottom=3 cm,footskip=2cm}
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes

params:
  Version: 1
classoption: table
---

\begin{center}
\end{center}

\vspace{6\baselineskip}

\newcolumntype{g}{>{\columncolor{red_AA}}c}

\begin{center}
\begin{tabular}{|g|l|}
\hline
\textcolor{black}{Project name} & Github Project \\
\textcolor{black}{\textit{ }} &  \\\hline
\textcolor{black}{R Software Version } & `r R.Version()$version.string` \\
\textcolor{black}{\textit{ }} &  \\\hline
\textcolor{black}{Version}  & V1 \\
\hspace{5cm} &\hspace{10cm} \\\hline
\textcolor{black}{Change description } & Initial redaction \\
\textcolor{black}{ } & \\ \hline
\end{tabular}

\vspace{4\baselineskip}

\begin{tabular}{|g|c|c|c|c|}
\hline
\rowcolor{red_AA} 
&\textcolor{black}{ \textit{First Name}}  &\textcolor{black}{\textit{Last Name}}   &\textcolor{black}{Date} \\
\rowcolor{red_AA} &  & &  \\\hline
\textcolor{black}{Written by }& Andrés & Acuña Marroquín & \today  \\ 
\textcolor{black} {\textit{}} &  &   & 
\\\hline
\end{tabular}

\vspace{4\baselineskip}

\end{center}

\newpage
\centering
\raggedright
\tableofcontents  

# Definitions 

+ **The standard deviation:** The standard deviation quantifies the variation within a set of measurements.
Must not be confused with the standard error. The standard deviation is the most used.


$$ \Large  s = \sqrt{\frac{\sum_{i= 1}^n (x - \bar{x})^2 }{ n - 1 }}   $$

+ **The standard error:** The  standard error quantifies the variation (standard deviation) of an estimated parameter (or statistic) from a sampling distribution. This is the distribution of the means. Can be estimated with a single set of measurments.

$$ \Large Standard\;Error = SE = \frac{s}{\sqrt{n}} $$

+ **The coefficient of variation:**  The coefficient of variation, also known as relative standard deviation, is a standardized measure of dispersion of a probability distribution. The coefficient of variation in absolute value : 

$$ CV = \frac{\sigma}{\overline{x}} $$

+ **The coefficient of variation in percentage :**

$$ CV_{\%} = \frac{\sigma}{\overline{x}}*100 $$

```{r, echo=FALSE, message=FALSE}

source("libraries.R")

```
 
\newpage

# Data presentation
## ToothGrowth

Descriptive statistics for the ToothGrowth data set included in R. 

```{r,results='asis', echo=FALSE }

## Data overview using a box plot, grouping by the categorical and ordinal variables ("supp" and "dose") the continuous variable "len"
ToothGrowth %>% 
  ggplot(aes(as.factor(dose), len,color = as.factor(dose))) +
  geom_boxplot(alpha = 0.3) + 
  geom_jitter(width = 0.2,height = 0) +
  facet_grid(~supp)+
  ylab("Tooth length") + xlab("Dose in milligrams/day") + theme(legend.position = "none")+
  labs(title = "The Effect of Vitamin C on Tooth Growth in Guinea Pigs", subtitle = "Supplement type (VC or OJ)") 
  

## Data overview using a table grouped as the box plot, giving some descriptive statistics.
ToothGrowth %>% 
  group_by(dose,supp) %>% 
  summarise(n = n(),mean= mean(len), sd = sd(len),median = median(len),min = min(len), max = max(len)) %>% 
  kable(caption = "Data Overview for the ToothGrowth data set", digits = 2,align = "c", booktabs = T,linesep = "")  

```

\newpage 

## Iris 

Descriptive statistics for the Iris data set included in R. 

```{r}

# Create scatterplot with multiple layers and facetting
ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point(aes(color = factor(cyl)), size = 4, alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed", color = "black") +
  facet_grid(vs ~ am) +
  labs(x = "Miles per Gallon", y = "Weight") +
  scale_color_discrete(name = "Cylinders") +
  theme_bw()

```


\newpage

# Session Info

```{r,echo=T}

sessionInfo()

```
