---
format: pdf
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
header-includes:
  - \usepackage{fancyhdr}
  - \usepackage{lastpage}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \lhead{Statistical Report}
  - \rhead{\thepage}
  - \cfoot[C]{{Page \thepage\ / \pageref{LastPage}}}
  - \usepackage{lipsum} % for sample text
  - \usepackage{hyperref} % for hyperlinks in table of contents
---

\begin{titlepage}
  \centering
  \vspace*{1cm}
  
  \Huge
  \textbf{Statistical Report}
  
  \vspace{0.5cm}
  \LARGE
  Data Analysis for GitHub profile
  
  \vspace{1.5cm}
  
  \textbf{Andrés Acuña Marroquín}
  
  \vfill
  
  A report submitted in partial fulfillment of the requirements for the degree of XYZ
  
  \vspace{0.8cm}
  
  \Large
  GitHub\\
  Date: 2024-05-27
  
  \vspace{0.5cm}
  \textbf{Project Name:} GitHub project
  
  \vspace{0.5cm}
  \textbf{R Software Version:} RStudio Version
  \vspace{0.2cm}
  \textbf{R Version:} 4.0.3 (2024-05-27)
  
  \vspace{0.5cm}
  \textbf{Change Description:}
  \begin{itemize}
    \item Initial version of the report
    \item Added statistical analysis section
    \item Revised conclusions based on latest data
  \end{itemize}
  
\end{titlepage}

\newpage
\centering
\raggedright
\tableofcontents  

# Introduction

\lipsum[1]

\newpage


# Definitions 

+ **The mean:** the sum of all values divided by the number of values.

$$ \overline{x} = \frac{1}{n} \sum_{i=1}^{n} x_i  $$ 

+ **The weigthed mean:** the sum of all values times a weight divided by the sum of the weights.

$$ \bar{x}_w = \frac{\sum_{i=1}^n w_i x_i}{\sum_{i=1}^n w_i} $$


+ **The standard deviation:** The standard deviation quantifies the variation within a set of measurements.
Must not be confused with the standard error. The standard deviation is the most used.


$$ \Large  s = \sqrt{\frac{\sum_{i= 1}^n (x - \bar{x})^2 }{ n - 1 }}   $$

+ **The standard error:** The  standard error quantifies the variation (standard deviation) of an estimated parameter (or statistic) from a sampling distribution. This is the distribution of the means. Can be estimated with a single set of measurments.

$$ \Large Standard\;Error = SE = \frac{s}{\sqrt{n}} $$

+ **The coefficient of variation:**  The coefficient of variation, also known as relative standard deviation, is a standardized measure of dispersion of a probability distribution. The coefficient of variation in absolute value : 

$$ CV = \frac{\sigma}{\overline{x}} $$

+ **The coefficient of variation in percentage :**

$$ CV_{\%} = \frac{\sigma}{\overline{x}}*100 $$

```{r, echo=FALSE, message=FALSE}

source("libraries.R")

```
 
\newpage

# Data presentation
## ToothGrowth

Descriptive statistics for the ToothGrowth data set included in R. 

```{r,results='asis', echo=FALSE }

## Data overview using a box plot, grouping by the categorical and ordinal variables ("supp" and "dose") the continuous variable "len"
ToothGrowth %>% 
  ggplot(aes(as.factor(dose), len,color = as.factor(dose))) +
  geom_boxplot(alpha = 0.3) + 
  geom_jitter(width = 0.2,height = 0) +
  facet_grid(~supp)+
  ylab("Tooth length") + xlab("Dose in milligrams/day") + theme(legend.position = "none")+
  labs(title = "The Effect of Vitamin C on Tooth Growth in Guinea Pigs", subtitle = "Supplement type (VC or OJ)") 
  

## Data overview using a table grouped as the box plot, giving some descriptive statistics.
ToothGrowth %>% 
  group_by(dose,supp) %>% 
  summarise(n = n(),mean= mean(len), sd = sd(len),median = median(len),min = min(len), max = max(len)) %>% 
  kable(caption = "Data Overview for the ToothGrowth data set", digits = 2,align = "c", booktabs = T,linesep = "")  

```

\newpage 

<!-- ## Diamonds -->

<!-- ```{r,results='asis', echo=FALSE,fig.height=4,,fig.width=4, fig.align='center' } -->

<!-- diamonds |>  -->
<!--   ggplot((aes(x=carat, y=price))) +  -->
<!--   geom_point( alpha=0.1) + -->
<!--   geom_density2d(colour="white")  + -->
<!--   scale_fill_gradient(low="white", high="black") + -->
<!--   labs(x="Carat", y="Price") -->


<!-- ``` -->


## QQ-Plot

```{r,results='asis', echo=FALSE,fig.height=4,,fig.width=4, fig.align='center'}


norm_samp <- rnorm(100)
qqnorm(norm_samp)
abline(a=0, b=1, col='grey')


```

\newpage

# Methods

\lipsum[3-4]

# Results

\lipsum[5-6]

# Discussion

\lipsum[7-8]

# Conclusion

\lipsum[9-10]

# References

\begin{thebibliography}{9}

\bibitem{latexcompanion} 
  Author, F. (Year). \textit{Book Title}. Publisher.

\bibitem{knuthwebsite} 
  Knuth, D. (Year). Title of paper. \textit{Journal Name}, Volume(Issue), Page numbers.

\end{thebibliography}
